The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
clarify comments on figure 5
Fig 1 caption changed to refer to eqns

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \arun{Give parameter values. Set
             minor ticks.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use
  thicker line width for the actual histogram.  Change legend to say
  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the
actual equation.  Also, why are two of the horizontal lines in the
bottom panel solid and one dashed?  What decides the style for each
line?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\subsection{Axis-ratios} 
We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
\subsubsection{Comparing distributions}
\begin{figure*}
 \centering
 \includegraphics[width=2.3\columnwidth]{axis_ratio_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table. \ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant. \rachel{This figure and the ones below appear to be right-justified (pushed up against the right margin) instead of centered.  Can you look into fixing that?  Also, the $:=$ is not very standard notation, I recommend just $=$.  Finally, the spacing in the legends is funny; I would prefer to see things like ``8213 (OD)'' rather than the current ``8213( OD )''.  The former is also consistent with the next figure.}}
 \label{fig:axisratio_all}
\end{figure*}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Give parameter values. Set
             minor ticks.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use  thicker line width for the actual histogram.  Change legend to say  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the actual equation.  Also, why are two of the horizontal lines in the bottom panel solid and one dashed?  What decides the style for eachline?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
\arun{Done. But I refer to the equations in the caption instead of the legend.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\subsection{Axis-ratios} 
We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
\subsubsection{Comparing distributions}
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{axis_ratio_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table. \ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant. \rachel{This figure and the ones below appear to be right-justified (pushed up against the right margin) instead of centered.  Can you look into fixing that?  Also, the $:=$ is not very standard notation, I recommend just $=$.  Finally, the spacing in the legends is funny; I would prefer to see things like ``8213 (OD)'' rather than the current ``8213( OD )''.  The former is also consistent with the next figure.}}
 \label{fig:axisratio_all}
\end{figure*}
